The human visual system preserves the hierarchy of 2-dimensional pattern regularity

### 2020-09-01 Writeup/manuscript.tex
The figures are back!
Added figure caption

\templatetype{pnasresearcharticle} % Choose template 
% {pnasresearcharticle} = Template for a two-column research article
% {pnasmathematics} %= Template for a one-column mathematics article
% {pnasinvited} %= Template for a PNAS invited submission

@@

\maketitle
\thispagestyle{firststyle}
\ifthenelse{\boolean{shortarticle}}{\ifthenelse{\boolean{singlecolumn}}{\abscontentformatted}{\abscontent}}{}

@@

\begin{figure}[tb]
\centering
\includegraphics[width=1\linewidth]{../figures/figure1.png}
\caption{Examples of each of the 16 wallpaper groups are shown in the left- and right-most column of the figures, next to the corresponding SSVEP (center-left) and psychological (center-right) data from each group. The SSVEP data are odd-harmonic-filtered cycle-average waveforms. In each cycle, a P1 exemplar was shown for the first 600 ms, followed by the original exemplar for the last 600 ms. Errorbars are standard error of the mean. Psychophysical data are presented as boxplots reflecting the distribution of display duration thresholds. The 16 groups are ordered by the strength of the SSVEP response, to highlight the range of response amplitudes.}
\label{fig:durations_rotations}
\end{figure}

@@

We also ran a control analysis using (1) odd-harmonic SSVEP data from a six-electrode ROI over parietal cortex (see Supplementary Figure 1.1) and (2) even-harmonic SSVEP data from the same occipital ROI that was used in our primary analysis. By comparing these two control analysis to our primary SSVEP analysis, we can address the specify of our effects in terms of location (occipital cortex vs parietal cortex) and harmonic (odd vs even). For both control analyses (plotted in Supplementary Figures 3.3 and 3.4), the correspondence between data and subgroup relationships was weaker than in the primary analysis. We can quantify the strength of the assocation between the data and the subgroup relationships, by asking what proportion of subgroup relationships that reach or exceed a range of probability thresholds. This is plotted in Figure 4, for our psychophysical data, our primary SSVEP analysis and our two control SSVEP analyses. It it that odd-harmonic SSVEP data from an occipital ROI and display duration thresholds both have a strong association with the subgroup relations, that for a clear majority of the subgroups survive even at the highest threshold we consider ($p(\Delta|data)>0.99$), and that the assocation is far weaker for the two control analyses.

@@

\begin{figure}[tbhp]
\centering
\includegraphics[width=1\linewidth]{../analysis/plots/model_roc_style.pdf}
\caption{}}
\label{fig:durations_rotations}
\end{figure}

>>>>

%\templatetype{pnasresearcharticle} % Choose template 
% {pnasresearcharticle} = Template for a two-column research article
% {pnasmathematics} %= Template for a one-column mathematics article
% {pnasinvited} %= Template for a PNAS invited submission
\usepackage{graphicx}

@@

% \maketitle
\thispagestyle{firststyle}
\ifthenelse{\boolean{shortarticle}}{\ifthenelse{\boolean{singlecolumn}}{\abscontentformatted}{\abscontent}}{}

@@

\begin{figure}[tbhp]
\centering
\includegraphics[width=1\linewidth]{../figures/figure1.png}
\caption{Examples of each of the 16 wallpaper groups are shown in the left- and right-most column of the figures, next to the corresponding SSVEP (center-left) and psychological (center-right) data from each group. The SSVEP data are odd-harmonic-filtered cycle-average waveforms. In each cycle, a P1 exemplar was shown for the first 600 ms, followed by the original exemplar for the last 600 ms. Errorbars are standard error of the mean. Psychophysical data are presented as boxplots reflecting the distribution of display duration thresholds. The 16 groups are ordered by the strength of the SSVEP response, to highlight the range of response amplitudes.}
\label{fig:durations_rotations}
\end{figure}

@@

We also ran a control analysis using (1) odd-harmonic SSVEP data from a six-electrode ROI over parietal cortex (see Supplementary Figure 1.1) and (2) even-harmonic SSVEP data from the same occipital ROI that was used in our primary analysis. By comparing these two control analysis to our primary SSVEP analysis, we can address the specify of our effects in terms of location (occipital cortex vs parietal cortex) and harmonic (odd vs even). For both control analyses (plotted in Supplementary Figures 3.3 and 3.4), the correspondence between data and subgroup relationships was weaker than in the primary analysis. We can quantify the strength of the assocation between the data and the subgroup relationships, by asking what proportion of subgroup relationships that reach or exceed a range of probability thresholds. This is plotted in Figure 4, for our psychophysical data, our primary SSVEP analysis and our two control SSVEP analyses. It it that odd-harmonic SSVEP data from an occipital ROI and display duration thresholds both have a strong association with the subgroup relations, that for a clear majority of the subgroups survive even at the highest threshold we consider ($p(\Delta>0|data)>0.99$), and that the assocation is far weaker for the two control analyses.

@@

\begin{figure}[tbhp]
\centering
\includegraphics[width=1\linewidth]{../analysis/plots/model_roc_style.pdf}
\caption{This plot shows the proportion of subgroup relations that satisfy $p(\Delta >0 | data) > x$. We can see that if we take $x = 0.95$ as our threshold, the subgroup relations are preserved in 56/63 = 89\% and 49/64 = 78\% of the comparisons for the primary EEG and display durations repectively. This compares to the 32/64= 50\% and 22/64 = 35\% for the control EEG conditions.}
\label{fig:durations_rotations}
\end{figure}
